---
title: "ESM 262 Looping Example Feb 16"
author: "Sarah Hamilton"
date: "2/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Try this - make a random sample of fertilizer application, 10 values with mean of 5 and standard deviation of 0.5
(user rnorm function in R to do this)
```{r}
fertilizer_ex = rnorm(mean = 5, sd = 0.5, n = 10)
```


Lets imagine that annual yield of a crop can be estimated follows:

yield=1.8∗fertilizer^2−0.5∗fertilizer+0.3∗TP

and TP is mean precipitation in cm

Use a for loop to compute the total yield after 10 years

- fertilizer is normally distributed with mean of 20 and standard deviation of 2
- TP is 20cm

```{r}
fertilizer_2 = rnorm(mean = 20, sd = 2, n =10)
tp_val = 20 

yield_df <- data.frame(fertilizer = fertilizer_2, tp = tp_val, yield = NA)

for (n in 1:10) {
  yield_df$yield = 1.8*yield_df$fertilizer^2 - 0.5*yield_df$fertilizer + 0.3*yield_df$tp
}

yield_total = sum(yield_df$yield)
```

Now create a function to that takes as input a single value for annual fertilizer and annual total precipitation and returns yield

```{r}
yield_function = function(annual_fertilizer, annual_precip) {
  yield_annual = 1.8*annual_fertilizer^2 - 0.5*annual_fertilizer + 0.3*annual_precip
}

#r = yield_function(10,20)
```

Now modify your function so that it returns total yield if the user inputs a vector of fertilizer and a vector of precipitation

```{r}
yield_function_vec = function(annual_fertilizer, annual_precip) {
  yield_total = 0
  for (n in length(annual_fertilizer)){
      yield_total = yield_total + (1.8*annual_fertilizer[n]^2 - 0.5*annual_fertilizer[n] + 0.3*annual_precip[n])
  }
  return(yield_total)
}

test_fertilizer = c(10,20,30)
test_precip = c(1,2,3)

test_yield = yield_function_vec(test_fertilizer, test_precip)
```


Check that function returns the same result as your original for loop Add some error checking and test

