---
title: "ESM 262 Assignment 6"
author: "Sarah Hamilton"
date: "3/2/2022"
output: html_document
---

Code to test extreme temperature risk function

Assignment:
Create a function that computes a level of risk associated with a extreme temperature events.

You can decide who/what the risk is to - for example risk of heat related illness for urban dwellers, or risk of heat related mortality for a particular type of tree

You function should take as input daily temperature data - from this data you should estimate how often extremes occur -

What is an extreme temperature? you should include a threshold to define extremes as one of the input parameters. You can be flexible here - if you want you can think of extremes as only occurring when you have temperature above a threshold for a sequence several days (and the number of days would be another parameter) or something simpler - just any temperature above a threshold; if you want you could have different thresholds to define different “severity” of extremes.

What is risk? You will develop the equation for risk on your own! Be creative here - what might make sense? how might temperature extremes translate into risk; would it be a linear equation- something else? What might be some of the parameters that influence risk (incomes, tree species, age? (include at least two parameters) How many categories of risk will you have

Have your function return both the risk associated with the input temperature sequence AND then number of extremes

Code your function in R Make sure you document well

Create an Rmarkdown to demonstrate the use of your function with tmax.txt - which is under Data on ESM_262_Examples

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(purrr)
```

```{r}
# source("~/Desktop/Bren Winter 2022/ESM 262/esm262-assignments-hamilton/R/temp_risk_score.R")

daily_temp <- read.table(file = "~/Desktop/Bren Winter 2022/ESM 262/esm262-assignments-hamilton/data/tmax.txt") %>%
  as.data.frame() %>%
  janitor::row_to_names(row_number = 1)

temp_vec <- as.double(daily_temp$tmax)

temp_results <- temp_risk_score(temp_vec)
```

